<!-- requires MxModel object assigned to .model -->

# {{ .label }} - Expected Data Summary

This model was fit on `r format(.model@output$timestamp, "%x at %I:%M%P")` using OpenMx v`r .model@output$mxVersion`.

## Free Parameter Estimates

This table shows a list of all the free parameters with their name, matrix element locators, parameter estimate and standard error, as well as lower and upper bounds if those were assigned. Note, `NA` is given for the name of elements that were not assigned a label. The columns **row** and **col** display the variables at the tail of the paths and the variables at the head of the paths, respectively.

```{r {{ .label }}-params-table, results='asis'}
.model_summary <- summary(.model)
kable(.model_summary$parameters) %>% 
  kable_styling(bootstrap_options = "condensed")
```

## Goodness of Fit Statistics

This tables includes the number of observed statistics, the number of estimated parameters, the degrees of freedom, minus twice the log-likelihood of the data, the number of observations, the chi-square and associated p-value and several information criteria.

```{r {{ .label }}-fit-table}
.model_summary %>% 
  table_gof() %>%
  kable() %>% 
  kable_styling(bootstrap_options = "condensed")
```
