<!-- requires MxModel object assigned to .model -->
# Observed Data Summary

```{r {{ .label }}-submodel-description, results='asis'}
intro <- sprintf("The observed data extracted from the %s model", .model$name)
if (smN(.model) == 1) {
  cat(intro, " included only a single submodel ", smNames(.model), ".", sep = "")
} else {
  cat(intro, " included ", smN(.model), " submodels.", sep = "")
}
```

## Summary Statistics

The following table provides summary statistics for each of the included variables:

```{r {{ .label }}-submodel-summary-stats, results='asis'}
smSummaries(.model) %>%
  kable(format.args = list(digits = 2)) %>%
  collapse_rows(columns = 1) %>%
  kable_styling(bootstrap_options = "condensed")
```

## Covariance Matrices

Pairwise correlations were calculated among all variables comprising each submodel. The upper-triangles contain pearson product-moment correlations between for numeric variables, polyserial correlations between numeric and ordinal variables, and polychoric correlations between ordinal variables; the lower-triangles contain p-values for tests of bivariate normality for each pair of variables.

```{r {{ .label }}-covar-calc}
sm.cors <- .model %>% 
  smData() %>% 
  map(polycor::hetcor, use = "pairwise.complete")
```

```{r {{ .label }}-covar-tables, results='asis'}
sm.cors %>% 
  map(spliceHetCor, values = c("tests", "correlations")) %>%
  map(formatC, digits = 3, width = -1) %>% 
  map(sub, pattern = "NA", replacement = "") %>% 
  iwalk(~ .x %>% 
          kable(caption = sprintf("%s correlations", .y)) %>% 
          kable_styling(bootstrap_options = "condensed") %>% 
          cat
  )
```
