---
title: OpenMx Analysis
output: 
  html_document: 
    toc: yes
    toc_depth: 1
---


# Introduction

This report is designed to help explore the results of an OpenMx analysis.

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
library(polycor)
library(purrr)
library(rlang)
suppressPackageStartupMessages(library(OpenMx))

opts_chunk$set(echo = FALSE)
options(knitr.table.format = "html")
```

```{r model-summaries, eval=TRUE}
# labels for chunk names and paths
.labels <- make.names(map_chr(.models, "name"))
names(.models) <- .labels

src <- mapply(knit_expand, .label = .labels, MoreArgs = list(file = system.file("modules/model-summary.Rmd", package = "mxtx")))
```

`r knit(text = unlist(src))`

## Free Parameters

This table shows a list of all the free parameters with their name, matrix element locators, parameter estimate and standard error, as well as lower and upper bounds if those were assigned. Note, `NA` is given for the name of elements that were not assigned a label. The columns **row** and **col** display the variables at the tail of the paths and the variables at the head of the paths, respectively.

```{r table-params}
model_summary <- summary(.models[[1]])
kable(model_summary$parameters)
```

## Goodness of Fit Statistics

This tables includes the number of observed statistics, the number of estimated parameters, the degrees of freedom, minus twice the log-likelihood of the data, the number of observations, the chi-square and associated p-value and several information criteria.

```{r table-gof}
kable(table_gof(model_summary))
```
