---
title: OpenMx Analysis
output: html_document
---


# Introduction

This report is designed to help explore the results of an OpenMx analysis. 

```{r setup, include=FALSE}
library(knitr)
suppressPackageStartupMessages(library(OpenMx))

opts_chunk$set(echo = FALSE)

model_summary <- summary(model)
```

# `r model$name` Model Summary

This model was fit on `r format(model@output$timestamp, "%x at %I:%M%P")` using OpenMx v`r AdeFit@output$mxVersion`.

## Free Parameters

This table shows a list of all the free parameters with their name, matrix element locators, parameter estimate and standard error, as well as lower and upper bounds if those were assigned. Note, `NA` is given for the name of elements that were not assigned a label. The columns **row** and **col** display the variables at the tail of the paths and the variables at the head of the paths, respectively.

```{r table-params}
kable(model_summary$parameters)
```

## Goodness of Fit Statistics

This tables includes the number of observed statistics, the number of estimated parameters, the degrees of freedom, minus twice the log-likelihood of the data, the number of observations, the chi-square and associated p-value and several information criteria.

```{r table-gof}
kable(table_gof(model_summary))
```

